Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-10 R0V0.tex
Item 11. See paragraph I.23

\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to the number of variables. However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.

>>>>

\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints. However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.
